Query Optimization for Dynamic Imputation

### 2017-03-01 paper/experiments.tex
paper: remove references to query 9

\begin{figure}
\todo{Relabel 9 somehow, since it is no longer in table of queries but in lined later}
\includegraphics[width=\columnwidth]{figures/running_times_combined_bar_13.png}
\caption{Query runtimes with imputation on base tables, \ProjectName{}
    optimizing for quality ($\alpha=0$), and \ProjectName{} optimizing for
    performance ($\alpha=1$). Quality-optimized, on-the-fly imputation provides an order of
    magnitude speedup over imputing on base tables. Efficiency-optimized on-the-fly
    imputation can provide another order-of-magnitude speedup at the expense of quality. For
    relatively expensive queries over large datasets (Query 9), runtime of imputation can be reduced
    from~\acsbaseresulthours~to~\acsimputedbzeroresult.}

@@

\subsubsection{Runtime of Base-table Imputation}
In many real-world cases, applying the imputation step at the base table is prohibitively
expensive.
To illustrate the increasing difficulty of such an approach as datasets scale, we ran the following query over the ACS dataset:
\begin{lstlisting}[breaklines]
SELECT AVG(c0) FROM acs_dirty;
\end{lstlisting}
Applying the imputation operation to the base table is extremely expensive, in our case
completing in \acsbaseresultminutes{} (\Cref{fig:runtimes}). In contrast, \ProjectName{} executes a quality-optimized version
in \acsimputedbzeroresult{} and a runtime-optimized version in \acsimputedboneresult{}. This highlights the potential
benefit of using our system for early data exploration.

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{figures/running_times_combined_bar_13.png}
\caption{Query runtimes with imputation on base tables, \ProjectName{}
    optimizing for quality ($\alpha=0$), and \ProjectName{} optimizing for
    performance ($\alpha=1$). Quality-optimized, on-the-fly imputation provides an order of
    magnitude speedup over imputing on base tables. Efficiency-optimized on-the-fly
    imputation can provide another order-of-magnitude speedup at the expense of quality.}

@@

\subsubsection{Runtime of Base-table Imputation}
In many real-world cases, applying the imputation step at the base table is prohibitively
expensive.
To illustrate the increasing difficulty of such an approach as datasets scale, we ran the following query over the ACS dataset:
\begin{lstlisting}[breaklines]
SELECT AVG(c0) FROM acs_dirty;
\end{lstlisting}
Applying the imputation operation to the base table is extremely expensive, in our case
completing in \acsbaseresultminutes{}. In contrast, \ProjectName{} executes a quality-optimized version
in \acsimputedbzeroresult{} and a runtime-optimized version in \acsimputedboneresult{}. This highlights the potential
benefit of using our system for early data exploration.
